### 2016-07-05 docs/ms_communitySynchrony_PREPRINT.tex
edits peer review disclosure to preprint
updates preprint for bioRxiv

\usepackage{setspace}
\usepackage{todonotes}
\usepackage{color}
\usepackage{rotating}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{\color{red}THIS MANUSCRIPT HAS NOT UNDERGONE PEER REVIEW}
\lhead{}
\rhead{}

@@

\begin{abstract}
Temporal asynchrony among species is an important mechanism through which diversity can stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific competition, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
Simulation experiments showed that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific competition and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding to environmental fluctuations (environmental
stochasticity), or fluctuating asynchronously because of random chance
events (demographic stochasticity) (Isbell et al. 2009, Hector et al.
2010, {{de Mazancourt}} et al. 2013). Species richness affects synchrony
because larger species pools are more likely to contain species that
respond disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014). Predicting the impacts of global
change requires a mechanistic understanding of species synchrony in
natural settings.

Theory identifies the three main determinants of species synchrony as
environmental stochasticity, demographic stochasticity, and
interspecific competition (Loreau and {{de Mazancourt}} 2008, 2013,
Gonzalez and Loreau 2009). For example, in a community composed of large
(no demographic stochasticity) and weakly interacting (no interspecific
competition) populations, community-wide species synchrony should be
determined by the covariance of species' responses to the environment
(Loreau and {{de Mazancourt}} 2008). However, such a prediction relies
on a relatively simple population model and only holds under two
assumptions: (i) species' responses to the environment are similar in
magnitude and (ii) all species have similar growth rates. Whether such
theoretical predictions hold in natural communities where species
differences are unlikely to be symmetrical remains unkown: no study has
explicitly tested theory on the drivers of species synchrony in natural
communities.

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from community time series (e.g.,
Houlahan et al. 2007) is impossible. This is because an unbiased null
expectation for synchrony does not exist (Loreau and {{de Mazancourt}}
2008) and observed synchrony can arise from non-unique combinations of
factors (Ranta et al. 2008). For example, weak synchrony of population
abundances could reflect positive environmental correlations
(synchronizing effect) offset by strong competition (desynchronizing
effect), or negative environmental correlations and weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific competition is to remove
them one-by-one, and in combination. In principle, this could be done in
an extremely controlled laboratory setting, but empirically-based models
of interacting populations, fit with data sets from natural communities,
offer a practical alternative. For example, Mutshinda et al. (2009) fit
a dynamic population model to several community time series of insect
and bird abundances. They used a statistical technique to decompose
temporal variation into competition and environmental components, and
found that postively correlated environmental responses among species
determined community dynamics. While a major step forward, Mutshinda et
al.'s (2009) modeling technique relied on abundance data that may or may
not reliably capture competitive interactions that occur at the
individual level. Furthermore, although Mutshinda et al. (2009)
quantified the relative importance of environmental stochasticity and
competition to explain the observed variation of species synchrony, they
did not use the model to quantify how much synchrony would change when
each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific competition on species synchrony in
natural plant communities. To achieve these objectives, we first refine
theory that has been used to predict the effects of species richness on
ecosystem stability ({{de Mazancourt}} et al. 2013) and species
synchrony (Loreau and {{de Mazancourt}} 2008) to generate predictions of
community-wide species synchrony under two limiting cases derived from
the dynamics of individual species in monoculture. We then confront our
theoretical predictions with simulations from the empirically-based
population models. Second, we use the multi-species population models to
perform simulation experiments that isolate the effects of environmental
stochasticity, demographic stochasticity, and interspecific competition
on community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

@@

Our study produced four main findings that were generally consistent
across five natural plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover, rather than
growth rates, were uninformative (Figs. S2-S3) since the linear
approximation required for analytical predictions is a stronger
assumption for abundance than growth rates, especially given relatively
short time-series (Online Supporting Information). Thus, our results
provide further evidence that it is difficult to decipher mechanisms of
species synchrony from abundance time series, as expected by theory
(Loreau and {{de Mazancourt}} 2008).

@@

Our theoretical predictions were derived from a simple model of
population dynamics and required several simplifying assumptions,
raising questions about their relevance to natural communities. However,
the theoretical predictions were strongly supported by simulations of
population models fit to long-term data from natural plant communities
(Table 3). Such a close match between our analytical predictions and the
simulation results should inspire confidence in the ability of simple
models to inform our understanding of species synchrony. The theoretical
population dynamical model we used here also successfully predicted
ecosystem stability in several biodiversity-ecosystem functioning
experiments ({{de Mazancourt}} et al. 2013).

@@

Demographic stochasticity partially counteracted the synchronizing
effects of environmental fluctuations and interspecific interactions on
per capita growth rates, but only when populations were small (Fig. 2),
in agreement with theory (Loreau and {{de Mazancourt}} 2008). Even in
small populations, however, demographic stochasticity was not strong
enough to completely counteract the synchronizing effects of
environmental fluctuations and match the analytical prediction where
only demographic stochasticity is operating (\(\mathcal{M}_D\) in Fig.
2). These results confirm the theoretical argument by Loreau and {{de
Mazancourt}} (2008) that independent fluctuations among interacting
species in a non-constant environment should be rare. Only in the Idaho
community does synchrony of per capita growth rates approach
\(\mathcal{M}_D\) in a non-constant environment (Fig. 2). This is most
likely due to the strong effect of demographic stochasticity on the
shrub \emph{Artemisia tripartita} since even a 5 \(\text{m}^2\) quadrat
would only contain a few individuals of that species.

@@

In large populations where interspecific interactions are weak,
synchrony is expected to be driven exclusively by environmental
fluctuations (Equation 4). Under such conditions community synchrony
should approximately equal the synchrony of species' responses to the
environment (Loreau and {{de Mazancourt}} 2008). Two lines of evidence
lead us to conclude that environmental fluctuations drive species
synchrony in our focal plant communities. First, in our simulation
experiments, removing interspecific interactions resulted in no
discernible change in community-wide species synchrony of per capita
growth rates (Fig. 1). Second, removing environmental fluctuations from
simulations consistently reduced synchrony (Fig. 1), and the synchrony
of species in monoculture was a very strong predictor of synchrony of
species in polyculture (Fig. 3). Our results lead us to conclude that
environmental fluctuations, not species interactions, are the primary
driver of community-wide species synchrony in the communities we
studied. Given accumulating evidence that niche differences in natural
communities are large (reviewed in Chu and Adler 2015), and thus species
interactions are likely to be weak, our results may be general in
natural plant communities.

In the Idaho community, removing environmental fluctuations did not
cause a large decrease in synchrony. However, that result appears to be
an artifact. Removing environmental variation results in a negative
invasion growth rate for \emph{A. tripartita}. Although we only analyzed
IBM runs in which \emph{A. tripartita} had not yet gone extinct, it was
at much lower abundance than in the other simulation runs. When we
removed \emph{A. tripartita} from all simulations, the Idaho results
conformed with results from all other sites: removing environmental
stochasticity caused a significant reduction in species synchrony (Fig.
S4). Our main results for Idaho (Fig. 2), with \emph{A. tripartita}
included, demonstrate how the processes that determine species synchrony
interact in complex ways. \emph{A. tripartita} has a facilitative effect
on each grass species across all vital rates, except for a small
competitive effect on \emph{H. comata}'s survival probability (Tables
S8-S10). At the same time, all the perennial grasses have negative
effects on each other for each vital rate (Tables S8-S10). We know
synchrony is affected by interspecific competition (Loreau and {{de
Mazancourt}} 2008), but how facilitative effects manifest themselves is
unknown. The interaction of facilitation and competition is clearly
capable of having a large effect on species synchrony, and future
theoretical efforts should aim to include a wider range of species
interactions.

A challenge to the generality of our results is that we were only able
to model common, co-occuring species (see Chu and Adler 2015). Rare
species, which our analysis does not include, could be kept at low
densities by competitive suppression due to strong interspecific
interactions. If we had been able to model rare species, we might have
found a larger effect of competition on community synchrony. However,
rare species may occupy rare niches that do not overlap with other
species, in which case synchrony would remain predominantly driven by
environmental responses. Rare species could also be limited by
generalist natural enemies whose effects are density-independent but
alter competitive hierarchies (Mordecai 2011). Under such conditions,
synchrony will depend on the degree of pathogen-induced fitness
differences and the pathogen's response to environmental conditions.
Neither our model nor current theory explicitly considers the effects of
pathogens on species synchrony, and this highlights the need for
theoretical work on the interaction between mechanisms of species
coexistence and mechanisms of species synchrony (Loreau 2010).

@@

We expected community synchrony of per capita growth rates to decrease
when we removed interspecific interactions (Loreau and {{de Mazancourt}}
2008). We found that community synchrony was virtually indistinguishable
between simulations with and without interspecific interactions (Fig.
2). The lack of an effect of interspecific competition on synchrony is
in contrast to a large body of theoretical work that predicts a strong
role for competition in creating compensatory dynamics (Tilman 1988) and
a recent empirical analysis (Gross et al. 2014).

@@

@@

This work was funded by the National Science Foundation through a
Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a
CAREER award to PBA (DEB-1054040). CdM and ML were supported by the
TULIP Laboratory of Excellence (ANR-10-LABX-41). We thank the original
mappers of the permanent quadrats at each site and the digitizers in the
Adler lab, without whom this work would not have been possible. Compute,
storage, and other resources from the Division of Research Computing in
the Office of Research and Graduate Studies at Utah State University are
gratefully acknowledged.

\subsection{STATEMENT OF AUTHORSHIP}
ATT, CdM, and PBA designed the research. CdM and ML designed and analyzed the theoretical model. ATT and PBA performed the empirical analysis. All authors contributed to the interpretation and presentation of results. ATT wrote the first draft of the manuscript, and all authors contributed to manuscript revisions.

\setlength{\parindent}{0ex} \newpage{}

@@

@@

@@

@@

Vellend, M., L. Baeten, I. H. Myers-Smith, S. C. Elmendorf, R.
Beauséjour, C. D. Brown, P. {De Frenne}, K. Verheyen, and S. Wipf. 2013.
Global meta-analysis reveals no net change in local-scale plant
biodiversity over time. Proceedings of the National Academy of Sciences
of the United States of America 110:19456--9.

@@

@@

\subsection{Table Titles}\label{tables}
TABLE 1: Site descriptions and focal species.

TABLE 2: Observed synchrony among species' per capita growth rates ($\phi_{R}$), observed synchrony among species' percent cover ($\phi_{C}$), the coefficient of variation of total community cover, and species richness for each community. Species richness values reflect the number of species analyzed from the community, not the actual richness.

\subsection{Tables}\label{tables}
\singlespacing

@@

\begin{table}[ht]
\centering
\caption{Observed synchrony among species' per capita growth rates ($\phi_{R}$), observed synchrony among species' percent cover ($\phi_{C}$), the coefficient of variation of total community cover, and species richness for each community. Species richness values reflect the number of species analyzed from the community, not the actual richness.} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & $\phi_{R}$ & $\phi_{C}$ & CV of Total Cover & Species richness \\ 
  \hline
New Mexico & 0.86 & 0.92 & 0.51 &   2 \\ 
  Arizona & 0.89 & 0.80 & 0.47 &   2 \\ 
  Kansas & 0.54 & 0.15 & 0.30 &   3 \\ 
  Montana & 0.53 & 0.58 & 0.54 &   4 \\ 
  Idaho & 0.36 & 0.18 & 0.19 &   4 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

\subsection{Figures Captions}
\doublespacing

FIGURE 1: Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. Error bars represent the upper and lower 95\% quantiles from model simulations. All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical prediction.

FIGURE 2: Synchrony of species' growth rates for each study area from IBM simulations across different landscape sizes when only demographic stochastcity is present (``D.S. Only'') and when environmental stochasticity is also present removed (``D.S. + E.S.''). The horizontal lines show the analytical predictions $\mathcal{M}_D$ (dashed line) and $\mathcal{M}_E$ (dotted line). The strength of demographic stochasticity decreases as landscape size increases because population sizes also increase. Theoretically, ``D.S. Only'' simulations should remain constant across landscape size, whereas ``D.S. + E.S.'' simulations should shift from the $\mathcal{M}_D$ prediction to the $\mathcal{M}_E$ prediction as landscape size, and thus population size, increases, but only if demographic stochasticity it strong enough to counteract environmental forcing. Error bars represent the upper and lower 95\% quantiles from model simulations.

FIGURE 3: Synchrony of species per capita growth rates simulated in large monocultures (IPM without species interactions) versus synchrony in large polycultures (IPM with species interactions). We used the same sequence of random year effects for both simulations (monoculture and polyculture) to mimic biodiversity-ecosystem functioning experiments. The dashed line is the line of equality. Simulation results in this figure are analogous to ``No Comp. + No D.S.'' (monocultures) and ``No D.S.'' (polycultures) in Fig. 1, but here we control the time series of random year effects.

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/formatted_figure1.png}
  \caption{Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. Error bars represent the upper and lower 95\% quantiles from model simulations. All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical prediction.}
\end{figure}

>>>>

\usepackage{setspace}
\usepackage{todonotes}
\usepackage{color}
\usepackage{rotating}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{\color{red}\textsf{THIS MANUSCRIPT HAS NOT UNDERGONE PEER REVIEW}}
\lhead{}
\rhead{}

@@

\begin{abstract}
Temporal asynchrony among species \textcolor{blue}{helps}\footnote{\textcolor{blue}{Changes and insertions unique to this version are shown in blue text.}} diversity \textcolor{blue}{to} stabilize ecosystem functioning, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific \textcolor{blue}{interactions}, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
\textcolor{blue}{We found} that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific \textcolor{blue}{interactions} and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding \textcolor{blue}{in different ways} to environmental
fluctuations (environmental stochasticity), or fluctuating
asynchronously because of random chance events (demographic
stochasticity) (Isbell et al. 2009, Hector et al. 2010, {{de
Mazancourt}} et al. 2013). Species richness affects synchrony because
larger species pools are more likely to contain species that respond
disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014).
\textcolor{blue}{The link between synchrony and stability means that a mechanistic understanding of synchrony can help us predict the impacts of global change on ecosystem stability.}

Theory identifies three main determinants of species synchrony:
environmental stochasticity, demographic stochasticity, and
\textcolor{blue}{interspecific interactions} (Loreau and {{de
Mazancourt}} 2008, 2013, Gonzalez and Loreau 2009). For example, in a
community composed of large \textcolor{blue}{populations} (no
demographic stochasticity)
\textcolor{blue}{with weak interspecific interations}, community-wide
species synchrony should be determined by the covariance of species'
responses to the environment (Loreau and {{de Mazancourt}} 2008).
However, \textcolor{blue}{this} prediction relies on a relatively simple
population model and only holds under two assumptions: (i) species'
responses to the environment are similar in magnitude and (ii) all
species have similar growth rates.
\textcolor{blue}{Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical is unkown because few studies have explicitly tested theory on the drivers of species synchrony in natural communities}
(Mutshinda et al. 2009, Thibaut et al. 2012),
\textcolor{blue}{and they did not consider demographic stochasiticity.}

In grasslands, most empirical studies have focused on whether species
synchrony is primarily an outcome of species-specific responses to
environmental conditions (Hautier et al. 2014) or competition (Gross et
al. 2014). Even beyond grassland studies, whether competition or
environmental responses drive compensatory dynamics remains
controversial (reviewed in Gonzalez and Loreau 2009). In part,
controversy remains because quantifying the relative strengths of each
driver on the degree of synchrony from
\textcolor{blue}{the covariance matrix of species abundances} (e.g.,
Houlahan et al. 2007) is impossible. This is because an unbiased null
expectation for synchrony does not exist (Loreau and {{de Mazancourt}}
2008) and observed synchrony can arise from non-unique combinations of
factors (Ranta et al. 2008). For example, weak synchrony of population
abundances could reflect positive environmental correlations
(synchronizing effect) offset by strong competition (desynchronizing
effect), or negative environmental correlations and weak competition.

The best way to quantify the effects of environmental stochasticity,
demographic stochasticity, and interspecific
\textcolor{blue}{interactions} is to remove them one-by-one, and in
combination. In principle, this could be done in an extremely controlled
laboratory setting, but empirically-based models of interacting
populations, fit with data sets from natural communities, offer a
practical alternative. For example, Mutshinda et al. (2009) fit a
dynamic population model to several community time series of insect and
bird abundances. They used a statistical technique to decompose temporal
variation into competition and environmental components, and found that
positively correlated environmental responses among species determined
community dynamics. Thibaut et al. (2012)
\textcolor{blue}{used a similar approach for reef fish and came to a similar conclusion: environmental responses determine synchrony.}
While a major step forward, Mutshinda et al.'s (2009) and Thibaut et
al.'s (2012) modeling technique relied on abundance data that may or may
not reliably capture competitive interactions that occur at the
individual level. Furthermore, although both studies quantified the
relative importance of environmental stochasticity and
\textcolor{blue}{interspecific interactions} to explain the observed
variation of species synchrony, they did not use the model to quantify
how much synchrony would change when each factor is removed.

Here, we use multi-species population models fit to long-term
demographic data from five semi-arid plant communities to test theory on
the drivers of species synchrony. Our objectives are to (1) derive and
test theoretical predictions of species synchrony and (2) determine the
relative influence of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
species synchrony in natural plant communities. To achieve these
objectives, we first refine theory that has been used to predict the
effects of species richness on ecosystem stability ({{de Mazancourt}} et
al. 2013) and species synchrony (Loreau and {{de Mazancourt}} 2008) to
generate predictions of community-wide species synchrony under two
limiting cases derived from the dynamics of individual species in
monoculture. We then confront our theoretical predictions with
simulations from the empirically-based population models. Second, we use
the multi-species population models to perform simulation experiments
that isolate the effects of environmental stochasticity, demographic
stochasticity, and interspecific \textcolor{blue}{interactions} on
community-wide species synchrony. Given that our population models
capture the essential features of community dynamics important to
synchrony (density-dependence, and demographic and environmental
stochasticity), and that these models successfully reproduce observed
community dynamics (Chu and Adler 2015), perturbing the models can
reveal the processes that determine species synchrony in our focal
grassland communities.

@@

Our study produced four main findings that were generally consistent
across five natural plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover, rather than
growth rates, were uninformative (Figs. S2-S3) since the linear
approximation required for analytical predictions is a stronger
assumption for abundance than growth rates, especially given relatively
short time-series (Online Supporting Information). Thus, our results
provide further evidence that it is difficult to decipher mechanisms of
species synchrony from abundance time series, as expected by theory
(Loreau and {{de Mazancourt}} 2008).
\textcolor{blue}{Observed synchrony of per capita growth rates was positively correlated with the variability of percent cover across our focal communities, which confirms that we are investigating an important process underlying ecosystem stability.}

@@

Our theoretical predictions were derived from a simple model of
population dynamics and required several simplifying assumptions,
raising questions about their relevance to natural communities.
\textcolor{blue}{For example, the species in our communities do not have equivalent environmental and demographic variances (Figs. S4-S7), as required by our predictions.}
However, the theoretical predictions
\textcolor{blue}{closely matched results from} simulations of population
models fit to long-term data from natural plant communities (Table 3).
Such \textcolor{blue}{strong agreement} between our analytical
predictions and the simulation results should inspire confidence in the
ability of simple models to inform our understanding of species
synchrony
\textcolor{blue}{even in complex natural communities, and allows us to place our simulation results within the context of contemporary theory}.

@@

Demographic stochasticity partially counteracted the synchronizing
effects of environmental fluctuations and interspecific interactions on
per capita growth rates, but only when populations were small (Fig. 2),
in agreement with theory (Loreau and {{de Mazancourt}} 2008). Even in
small populations, however, demographic stochasticity was not strong
enough to \textcolor{blue}{compensate} the synchronizing effects of
environmental fluctuations and match the analytical prediction where
only demographic stochasticity is operating (\(\mathcal{M}_D\) in Fig.
2). These results confirm the theoretical argument by Loreau and {{de
Mazancourt}} (2008) that independent fluctuations among interacting
species in a non-constant environment should be rare. Only in the Idaho
community does synchrony of per capita growth rates approach
\(\mathcal{M}_D\) in a non-constant environment (Fig. 2). This is most
likely due to the strong effect of demographic stochasticity on the
shrub \emph{Artemisia tripartita} since even a \textcolor{blue}{2}5
\(\text{m}^2\) quadrat would only contain a few individuals of that
species.

@@

In large populations where interspecific interactions are weak,
synchrony is expected to be driven exclusively by environmental
fluctuations (Equation 4). Under such conditions community synchrony
should approximately equal the synchrony of species' responses to the
environment (Loreau and {{de Mazancourt}} 2008). Two lines of evidence
lead us to conclude that environmental fluctuations drive species
synchrony in our focal plant communities. First, in our simulation
experiments, removing interspecific interactions resulted in no
discernible change in community-wide species synchrony of per capita
growth rates (Fig. 1). Second, removing environmental fluctuations from
simulations consistently reduced synchrony (Fig. 1), and the synchrony
of species in isolation was a very strong predictor of synchrony of
species in polyculture (Fig. 3). Our results lead us to conclude that
environmental fluctuations, not species interactions, are the primary
driver of community-wide species synchrony in the communities we
studied. Given accumulating evidence that niche differences in natural
communities are large (reviewed in Chu and Adler 2015), and thus species
interactions are likely to be weak, our results may be general in
natural plant communities.

In the Idaho community, removing environmental fluctuations did not
cause a large decrease in synchrony. However, that result appears to be
an artifact. Removing environmental variation results in a negative
invasion growth rate for \emph{A. tripartita}. Although we only analyzed
IBM runs in which \emph{A. tripartita} had not yet gone extinct, it was
at much lower abundance than in the other simulation runs. When we
removed \emph{A. tripartita} from all simulations, the Idaho results
conformed with results from all other sites: removing environmental
stochasticity caused a significant reduction in species synchrony (Fig.
S8). Our main results for Idaho (Fig. 2), with \emph{A. tripartita}
included, demonstrate how the processes that determine species synchrony
interact in complex ways. \emph{A. tripartita} has a facilitative effect
on each grass species across all vital rates, except for a small
competitive effect on \emph{H. comata}'s survival probability (Tables
S8-S10). At the same time, all the perennial grasses have negative
effects on each other for each vital rate (Tables S8-S10). We know
synchrony is affected by interspecific competition (Loreau and {{de
Mazancourt}} 2008), but how facilitative effects manifest themselves is
unknown. The interaction of facilitation and competition is clearly
capable of having a large effect on species synchrony, and future
theoretical efforts should aim to include a wider range of species
interactions.

A challenge to the generality of our results is that we were only able
to model common, co-occuring species (see Chu and Adler 2015).
\textcolor{blue}{Most communities are dominated by few common species and many rare species}
(McGill et al. 2007),
\textcolor{blue}{meaning that the low number of common species in our focal commiunities is not unusual.}
\textcolor{blue}{Rather, the generality of our results hinges upon the influence of rare species.
Rare species could be kept at low densities by competitive suppression due to strong interspecific interactions.
If we had been able to model rare species, we might have found a larger effect of competition on community synchrony.
However, recent theory predicts that persistent rare species may actually experience even weaker interspecific competition, and thus stronger niche differences, than common species}
(Yenni et al. 2012),
\textcolor{blue}{in which case synchrony would remain predominantly driven by environmental responses.}
Rare species could also be limited by generalist natural enemies whose
effects are density-independent but alter competitive hierarchies
(Mordecai 2011). Under such conditions, synchrony will depend on the
degree of pathogen-induced fitness differences and the pathogen's
response to environmental conditions. Neither our model nor current
theory explicitly considers the effects of pathogens on species
synchrony, and this highlights the need for theoretical work on the
interaction between mechanisms of species coexistence and mechanisms of
species synchrony (Loreau 2010).

@@

We expected community synchrony of per capita growth rates to decrease
when we removed interspecific interactions (Loreau and {{de Mazancourt}}
2008). We found that community synchrony was virtually indistinguishable
between simulations with and without interspecific interactions (Fig.
2). The lack of an effect of
\textcolor{blue}{interspecific interactions} on synchrony is in contrast
to a large body of theoretical work that predicts a strong role for
competition in creating compensatory dynamics (Tilman 1988) and a recent
empirical analysis (Gross et al. 2014).

@@

\textcolor{blue}{Our conclusion that species interactions have little impact on synchrony only applies to single trophic level communities.
Species interactions almost certainly play a strong role in multi-trophic communities where factors such as resource overlap}
(Vasseur and Fox 2007), \textcolor{blue}{dispersal} (Gouhier et al.
2010), \textcolor{blue}{and the strength of top-down control} (Bauer et
al. 2014)
\textcolor{blue}{are all likely to affect community synchrony.}

@@

This work was funded by the National Science Foundation through a
Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a
CAREER award to PBA (DEB-1054040). CdM and ML were supported by the
TULIP Laboratory of Excellence (ANR-10-LABX-41). We thank the original
mappers of the permanent quadrats at each site and the digitizers in the
Adler lab, without whom this work would not have been possible. Compute,
storage, and other resources from the Division of Research Computing in
the Office of Research and Graduate Studies at Utah State University are
gratefully acknowledged. We also thank three anonymous reviewers who
provided critical feedback that improved the manuscript.

\setlength{\parindent}{0ex}

@@

Bauer, B., M. Vos, T. Klauschies, and U. Gaedke. 2014. Diversity,
Functional Similarity, and Top-Down Control Drive Synchronization and
the Reliability of Ecosystem Function. The American Naturalist
183:394--409.

@@

McGill, B. J., R. S. Etienne, J. S. Gray, D. Alonso, M. J. Anderson, H.
K. Benecha, M. Dornelas, B. J. Enquist, J. L. Green, F. He, A. H.
Hurlbert, A. E. Magurran, P. A. Marquet, B. A. Maurer, A. Ostling, C. U.
Soykan, K. I. Ugland, and E. P. White. 2007. Species abundance
distributions: Moving beyond single prediction theories to integration
within an ecological framework. Ecology Letters 10:995--1015.

@@

Thibaut, L. M., S. R. Connolly, and H. P. A. Sweatman. 2012. Diversity
and stability of herbivorous fishes on coral reefs. Ecology 93:891--901.

@@

Vasseur, D. A., and J. W. Fox. 2007. Environmental fluctuations can
stabilize food web dynamics by increasing synchrony. Ecology Letters
10:1066--1074.

Vellend, M., L. Baeten, I. H. Myers-Smith, S. C. Elmendorf, R.
Beaus{é}jour, C. D. Brown, P. {De Frenne}, K. Verheyen, and S. Wipf.
2013. Global meta-analysis reveals no net change in local-scale plant
biodiversity over time. Proceedings of the National Academy of Sciences
of the United States of America 110:19456--9.

@@

Yenni, G., P. B. Adler, and S. K. {Morgan Ernest}. 2012. Strong
self-limitation promotes the persistence of rare species. Ecology
93:456--461.

@@

\subsection{Tables}\label{tables}

@@

\begin{table}[ht]
\centering
\caption{Observed synchrony among species' per capita growth rates ($\phi_{R}$), observed synchrony among species' percent cover ($\phi_{C}$), the coefficient of variation of total community cover, and species richness for each community. Species richness values reflect the number of species analyzed from the community, not the actual richness.} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & $\phi_{R}$ & $\phi_{C}$ & CV of Total Cover & Species richness \\ 
  \hline
New Mexico & 0.86 & 0.92 & 0.51 &   2 \\ 
  Arizona & 0.89 & 0.80 & 0.47 &   2 \\ 
  Kansas & 0.54 & 0.15 & 0.30 &   3 \\ 
  Montana & 0.53 & 0.54 & 0.52 &   4 \\ 
  Idaho & 0.36 & 0.18 & 0.19 &   4 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/formatted_figure1.png}
  \caption{Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific interactions present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific interactions removed (``No Comp.''), interspecific interactions and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific interactions and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. \textcolor{blue}{Error bars represent the 2.5\% and 97.5\% quantiles from model simulations.} All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical predicion.}
\end{figure}
